---
title: "Figures for The *Spatial Structure of Segregation*"
author: "Phil Chodrow"
date: "1/22/2017"
output: 
  html_document:
    theme: journal
    toc: true
    toc_float: true
---

# Introduction

The purpose of this document is to generate and lightly explain the figures used in "The Spatial Structure of Segregation." For more complete documentation, please see the technical report. 

# Setup

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE, fig.height = 4, fig.width = 6)
```


```{r}
library(tidyverse)
library(rgeos)
library(maptools)
library(scales)
library(ggthemes)
library(ggrepel)
library(igraph)
library(compx)
library(RColorBrewer)
library(gplots)
library(viridis)
library(ggmap)
```

```{r}
if(!dir.exists('figs')){
    dir.create('figs')
}
```


# Metric Structure

First we read in the data...
```{r}

city     <- 'Detroit'
input    <- readRDS(paste0('throughput/metric/', city, '.RDS'))
f_tracts <- input$tracts %>%
    fortify(region = 'GEOID')

metric_df <- input$metric_df 

f_tracts <- f_tracts %>% 
    left_join(metric_df, by = c('id' = 'geoid')) 
```

And now we plot. 

```{r}
# the tr/4 is from our existence theorem
f_tracts %>% 
    ggplot() + 
    aes(x = long, y = lat, fill = tr/4, group = group) + 
    geom_polygon() + 
    scale_fill_viridis(option = 'magma' , 
                                trans = 'log10',
                       limits = c(NA, 12e-1),
                                oob = squish) +
    theme_map() + 
    theme(legend.justification = c(0,0), 
          legend.position      = c(.8,.1),
          panel.background = element_rect(fill = 'grey80', color = NA),
          legend.background = element_rect(fill = NA)) + 
    guides(fill = guide_colorbar(ticks = F, title = expression(tr~italic(g[x]))))

ggsave('figs/local_density.pdf')

```

## Comparative Information Density

```{r}
scatterplot_theme <- function(){
     layout <- theme_bw() %+replace%
         theme(axis.ticks.y = element_line(size = 0, color = 'black'),
          axis.ticks.x = element_line(size = .2, color = 'black'),
          axis.ticks.length=unit(-0.25, "cm"), 
          axis.text.x = element_text(size = 11, margin=unit(c(0.5,0.5,0.5,0.5), "cm")), 
          axis.text.y = element_text(size = 11, margin=unit(c(0.5,0.5,0.1,0.5), "cm")),
          axis.title.y = element_text(margin=unit(c(0.1,-0.5,0.1,0.1), "cm"), angle = 90),
          axis.title.x = element_text(margin=unit(c(0,0,-0.1,-1), "cm"))) 
    
    list(layout)
}
```


```{r}

summary <- read_csv('throughput/metric.csv')

# summary <- summary %>% 
#     mutate(p_vol = p_vol / max(p_vol),
#            p_trace = p_trace / max(p_trace))

highlight <- summary %>% 
    filter(I_XY < 0 | I_XY > .35) 


 summary %>% 
    ggplot() + 
    aes(x = p_vol, y = p_trace) + 
    scale_y_continuous(trans = 'log10') +
    scale_x_continuous(trans = 'log10') +
    geom_point(color = 'grey') + 
    geom_point(color = 'firebrick', data = highlight) + 
    geom_text_repel(aes(label = city), data = highlight) +
    scatterplot_theme() + 
    xlab(expression(italic(E[X]) ~ sqrt(~det~g[X]))) + 
    ylab(expression(italic(E[X]) ~ (tr ~~  g[X]))) + 
    annotation_logticks(scaled = TRUE, size = .2, sides = 'lb')
    
 
 ggsave('figs/average_geometry.pdf')

```


```{r}
summary <- read_csv('throughput/metric.csv')

highlight <- summary %>% 
    filter(I_XY < 0 | I_XY > .35) 

summary %>% 
    ggplot() + 
    aes(x = I_XY, y = p_trace) + 
    scale_y_continuous(trans = 'log10') + 
    geom_point(color = 'grey') + 
    geom_point(color = 'firebrick', data = highlight) + 
    geom_text_repel(aes(label = city), data = highlight) +
    scatterplot_theme() + 
    ylab(expression(italic(E[X]) ~ (tr ~~  g[X]))) + 
    xlab(expression(italic(I(X,Y)))) + 
    annotation_logticks(scaled = TRUE, size = .2, sides = 'l') + 
    
ggsave('figs/density_mutual.pdf')
```

# Network Structure

## Spectra
```{r}
spectra <- read_csv('throughput/spectra.csv')

cities <- c('Philadelphia', 'Detroit', 'Atlanta', 'Chicago', 'New York City')
highlight <- spectra %>% 
    filter(city %in% cities)
```

```{r}

spectra_theme <- function(){
    
    layout <- theme_bw() %+replace%
    theme(axis.ticks.y = element_line(size = .2, color = 'black'),
          axis.ticks.x = element_line(size = .2, color = 'black'),
          axis.ticks.length=unit(-0.25, "cm"),
          axis.text.x = element_text(size = 11, margin=unit(c(0.5,0.5,0.5,0.5), "cm")), 
          axis.text.y = element_text(size = 11, margin=unit(c(0.5,0.5,0.1,0.0), "cm")),
          axis.title.y = element_text(margin=unit(c(0.1,-0.1,0.5,0.5), "cm"), angle = 90)
          ) 
    
    list(layout, 
         scale_color_brewer(palette = 'Set1'),
         guides(color = guide_legend(title = element_blank())))
    # scale_color_brewer(palette = 'Set1') %+replace% 
    # guides(color = guide_legend(title = element_blank())) 
}

```



```{r}

spectra %>% 
    ggplot() + 
    aes(x = n, y = 1-eig, group = city) + 
    geom_line(color = 'grey', alpha = 1, size = .3) + 
    scale_y_continuous(trans = 'log10', limit = c(8e-2, NA), expand=c(0,0)) + 
    scale_x_continuous(limit = c(0, 100), expand=c(0,0)) + 
    geom_line(aes(color = city),  data = highlight, size = 1) + 
    geom_point(data = highlight, size = .1, color = 'black') + 
    ylab(expression(1-lambda[italic(n)])) + 
    xlab(expression(italic(n))) + 
    annotation_logticks(scaled = T, sides = 'l', size = .2) +
    spectra_theme() + 
    theme(axis.ticks.y = element_line(size = 0, color = 'black'))
    

ggsave('figs/spectra.pdf')

```

## Differenced Spectra
```{r}

spectra <- spectra %>% 
    mutate(diff = lead(eig) / eig)

highlight <- spectra %>%
    filter(city %in% cities)

spectra %>% 
    ggplot() + 
    aes(x = n, y = diff, group = city) + 
    geom_line(alpha = .5, color = 'grey') +
    geom_line(aes(color = city), data = highlight, size = .7) + 
    geom_point(data = highlight, size = .5, color = 'black') +
    scale_x_continuous(limits = c(2, 25)) +
    scale_y_continuous(limits = c(1, 3.5)) +
    ylab(expression(lambda[italic(n+1)] /lambda[italic(n)])) +
    xlab(expression(italic(n))) + 
    spectra_theme()

ggsave('figs/spectra_differenced.pdf')

```

What happens when we incorporate area?

```{r, echo = FALSE, eval = FALSE}

area_df <- summary %>% 
    select(city, total_area)

spectra <- spectra %>% 
    # left_join(area_df) %>% 
    group_by(city) %>%
    mutate(scale = n/max(n)) %>% 
    ungroup()

spectra <- spectra %>% 
    mutate(diff = (1-eig) / (1-lead(eig)))

highlight <- spectra %>%
    filter(city %in% cities, scale < .1)

spectra %>% 
    filter(scale <= .1) %>%
    ggplot() + 
    aes(x = scale, y = diff, group = city) + 
    # geom_point(size = 2) + 
    geom_line(color = 'grey') + 
    geom_line(aes(color = city),  data = highlight, size = 1) +
    # geom_point(data = highlight, size = 1, color = 'black') + 
    # scale_x_continuous(limits = c(1, 30)) +
    scale_y_continuous(limits = c(1, 3.7)) +
    theme_bw() + 
    # ylab(expression(1-lambda[italic(n)])) + 
    xlab(expression(italic(n))) + 
    # annotation_logticks(scaled = T, sides = 'l', size = .2) + 
    theme(axis.ticks.y = element_line(size = .2, color = 'black'),
          axis.ticks.x = element_line(size = .2, color = 'black'),
          legend.position = 'bottom') + 
    ggtitle('Spectra of selected cities') + 
    scale_color_brewer(palette = 'Set1') + 
    guides(color = guide_legend(title = element_blank())) 




```

What about when we normalize n? 


```{r}

normed_spectra <- spectra %>%
    group_by(city) %>% 
    mutate(n = n/max(n))

normed_highlight <- normed_spectra %>% 
    filter(city %in% cities)

normed_spectra %>% 
    ggplot() + 
    aes(x = n, y = 1-eig, group = city) + 
    geom_line(color = 'grey', alpha = 1, size = .3) + 
    scale_y_continuous(trans = 'log10', limit = c(1e-1, NA), expand=c(0,0)) + 
    scale_x_continuous(limit = c(0.001, .5), expand=c(0,0), trans = 'log10') +
    geom_line(aes(color = city),  data = normed_highlight, size = 1) + 
    geom_point(data = normed_highlight, size = .3, color = 'black') + 
    theme_bw() + 
    ylab(expression(1-lambda[italic(n)])) + 
    xlab(expression(italic(n))) + 
    annotation_logticks(scaled = T, sides = 'l', size = .2) + 
    theme(axis.ticks.y = element_line(size = .2, color = 'black'),
          axis.ticks.x = element_line(size = .2, color = 'black'),
          legend.position = 'bottom') + 
    ggtitle('Spectra of selected cities') + 
    scale_color_brewer(palette = 'Set1') + 
    guides(color = guide_legend(title = element_blank())) 

ggsave('figs/normed_spectra.pdf')

```


```{r}

spectral_properties <- spectra %>% 
    group_by(city) %>% 
    filter(n >= 10 | eig  > 1e-10) %>% 
    filter(eig < 1) %>% 
    summarise(aff_trace =   sum( 1 - eig),
              aff_det   = - sum(log(1-eig))) %>%
    arrange(desc(aff_trace))

spectral_properties %>% 
    left_join(summary, by = c('city' = 'city')) %>% 
    ggplot() + 
    aes(x = aff_trace, y = total_vol) + 
    geom_point() +
    geom_text_repel(aes(label = city)) + 
    scale_y_continuous(trans = 'log10') + 
    scale_x_continuous(trans = 'log10') + 
    geom_smooth() + 
    ggtitle('Correlation between the trace of the affinity matrix and information volume.')

```

## Clustering

First we'll do ths clustering. 
```{r, fig.height = 6, fig.width = 10}
g <- readRDS(paste0('throughput/graphs/',city,'.RDS'))
A <- affinity_matrix(g, sigma = 1)
sigma <- 1
clust <- hclust(as.dist(-A),  method = 'complete')
pal   <- brewer.pal(9, name = "Set1") %>%
	colorRampPalette()

ncluster <- 7
g <- g %>% set_vertex_attr(name = 'cluster', index = colnames(A), value = clust %>% cutree(ncluster))

```

## Geodesics and Space Distortion

```{r}
k <- 600
center <- V(g)[[k]]$name
center_coords <- data_frame(x = V(g)[[k]]$x, y = V(g)[[k]]$y)

dists <- g %>% igraph::distances(weights = E(g)$dist)

dist_lookup <- dists[,center] %>% 
    as.data.frame() %>% 
    rownames_to_column(var = 'geoid') 

names(dist_lookup) <- c('geoid', 'dist')

f_tracts %>% 
    left_join(dist_lookup, by = c('id' = 'geoid')) %>% 
    ggplot() + 
    aes(x = long, y = lat, group = group, fill = dist) %>% 
    geom_polygon() + 
    scale_fill_viridis(option = 'magma' , 
                                oob = squish) +
    theme_map() + 
    theme(legend.justification = c(0,0), 
          legend.position      = c(.8,.1),
          panel.background = element_rect(fill = 'grey80', color = NA),
          legend.background = element_rect(fill = NA)) + 
    guides(fill = guide_colorbar(ticks = F, title = expression(d[gamma]))) + 
    geom_point(aes(x,y), data = center_coords, color = 'white')
    
ggsave('figs/geo_distance.pdf')
```

## Bare network structure

Visualization of network structure in Detroit. The weight of each line segment is proportional to the affinity between the tracts it connects. 
```{r}
edges <- g %>% as_long_data_frame() %>% tbl_df()
nodes <- data_frame(x = V(g)$x, y = V(g)$y, cluster = as.character(V(g)$cluster))

ggplot() + 
    geom_polygon(aes(x = long, y = lat, group = group), fill = 'grey10', alpha = .7, data = f_tracts) +
    geom_segment(aes(x = from_x, y = from_y, xend = to_x, yend = to_y, size = exp(-7 * dist^2), alpha = exp(-7 * dist^2)), color = 'white', data = edges) +
    theme_map() +
    scale_size_continuous(range = c(0,.5)) + 
    guides(alpha = 'none', color = 'none', size = 'none') +
    theme(panel.background = element_rect(fill = 'grey80', color = NA))

ggsave('figs/network_structure.pdf')

```

Now we'll have the color of the edge proportional to its geodesic distance. 

```{r}
edges <- g %>% as_long_data_frame() %>% tbl_df()
nodes <- data_frame(x = V(g)$x, y = V(g)$y, cluster = as.character(V(g)$cluster))

ggplot() + 
    geom_polygon(aes(x = long, y = lat, group = group), fill = 'grey80', alpha = .6, data = f_tracts) +
    geom_segment(aes(x = from_x, y = from_y, xend = to_x, yend = to_y, color = dist), data = edges) +
    theme_map() +
    scale_color_viridis(option = 'magma', trans = 'log10') + 
    guides(alpha = 'none', color = 'none', size = 'none') +
    theme(panel.background = element_rect(fill = 'grey80', color = NA))

ggsave('figs/network_structure_colored.pdf')

```


This one is a little bit busier, but shows fairly nicely how the network is most strongly separated at points of high curvature. 


```{r}
edges <- g %>% as_long_data_frame() %>% tbl_df()
nodes <- data_frame(x = V(g)$x, y = V(g)$y, cluster = as.character(V(g)$cluster))

ggplot() + 
    geom_polygon(aes(x = long, y = lat, fill = vol/area, group = group), data = f_tracts) + 
    scale_fill_viridis(option = 'magma' , 
                                trans = 'log10', 
                                oob = squish) +
    geom_segment(aes(x = from_x, y = from_y, xend = to_x, yend = to_y, size = exp(-10 * dist)), color = 'white', data = edges) +
    theme_map() +
    scale_size_continuous(range = c(0,1)) + 
    guides(alpha = 'none', color = 'none', size = 'none') +
    theme(panel.background = element_rect(fill = 'grey80', color = NA),
          legend.justification = c(0,0), 
          legend.position      = c(.8,.1),
          legend.background = element_rect(fill = NA)) + 
    guides(fill = guide_colorbar(ticks = F, title = expression(rho)))

ggsave('figs/network_structure_curvature.pdf')
```


Now let's do it with spectral clustering. 

```{r}

A <- affinity_matrix(g, sigma = 2)
L <- generalized_laplacian_matrix(A)
evL <- eigen(L, symmetric=TRUE)

# let's pick a number of clusters by checking out the spectrum. 
test_df <- data_frame(n = 1:nrow(A), eig = rev(evL$values)) %>% 
	mutate(eig = eig - min(eig),
		   eig = eig / max(eig)) %>% 
	mutate(val = lead(eig) / eig) %>% 
	filter(n < 50)
	
plot(test_df$val, log = 'y')

```



```{r}

make_clusters <- function(k, nreps = 1000){
    Z <- evL$vectors[,(ncol(evL$vectors)-k+1):(ncol(evL$vectors))]
    
    models <- data_frame(n = 1:nreps) %>% 
    	dplyr::mutate(model = map(n, ~ kmeans(Z, centers = k))) %>% 
    	mutate(perf = map_dbl(model, ~.$tot.withinss))
    
    model <- models %>% 
    	filter(perf == min(perf))
    km <- model$model[[1]]
    return(km$cluster)
}

get_node_df <- function(k){
    h <- g %>% set.vertex.attribute('cluster', value = make_clusters(k)) 
    data_frame(geoid = V(h)$name, 
               x = V(h)$x, 
               y = V(h)$y, 
               cluster = V(h)$cluster, 
               k = k)
}


```



```{r}

ks <- c(2, 6, 10, 15)

clusters <- ks %>% 
    map(get_node_df) %>% 
    reduce(rbind)

pal <- brewer_pal(palette = 'Set1')
pal <- colorRampPalette(pal(9))
pal <- pal(max(ks))

ggplot() + 
	geom_segment(aes(x = from_x, y = from_y, xend = to_x, yend = to_y, size = exp(-5 * dist^2)), color = 'black', alpha = .5, data = edges) +
	theme_map() +
	scale_size_continuous(range = c(0,1)) + 
	guides(alpha = 'none', color = 'none', size = 'none') +
	theme(panel.background = element_rect(fill = 'grey80', color = NA)) + 
	geom_point(aes(x, y, color = as.character(cluster)), data = clusters) + 
    scale_color_manual(values = pal) + 
    facet_wrap(~k, nrow = 3)

ggsave('figs/spectral_clustered.pdf')

```

```{r}

label_generator <- function(variable, value){
    return(paste0('k = ', value))
}

f_tracts %>% 
    left_join(clusters, by = c('id' = 'geoid')) %>% 
    ggplot() + 
    aes(x = long, y = lat, fill = as.character(cluster), group = id) + 
    facet_wrap(~k, nrow = 2, labeller = label_generator) + 
    geom_polygon() + 
    theme_map() +
    theme(panel.background = element_rect(fill = 'grey80', color = NA)) + 
    scale_fill_manual(values = pal) +
    guides(fill = FALSE) 

ggsave('figs/clustered_maps.pdf')
    

```




## Matrix Structure

Now let's visualize the affinity matrix! We can use hierarchical clustering for this task. 

```{r}
sigma = 1
affinity_matrix_viz <- function(city){
    g <- readRDS(paste0('throughput/graphs/',city,'.RDS'))
    A <- affinity_matrix(g, sigma = sigma)
    
    clust <- hclust(as.dist(-A),  method = 'complete')
    
    the_order <- data_frame(geoid = clust$labels[clust$order], order = 1:length(clust$labels))
    
    A %>% 
        as.data.frame() %>% 
        rownames_to_column('geoid_1') %>% 
        tbl_df() %>% 
        gather(geoid_2, a, -geoid_1) %>% 
        left_join(the_order, by = c('geoid_1' = 'geoid')) %>% 
        dplyr::rename(x = order) %>%
        left_join(the_order, by = c('geoid_2' = 'geoid')) %>% 
        dplyr::rename(y = order) %>% 
        ggplot() + 
        aes(x = x, y = y, fill = a) + 
        geom_raster() + 
        scale_fill_viridis(option = 'viridis') + 
        # theme_map() +
        theme(legend.position = 'right',
              axis.line=element_blank(),
              axis.text.x=element_blank(),
              axis.text.y=element_blank(),
              axis.ticks=element_blank(),
              axis.title.x=element_blank(),
              axis.title.y=element_blank()) + 
        scale_x_continuous(expand = c(0,0)) + 
        scale_y_continuous(expand = c(0,0)) + 
        guides(fill = guide_colorbar(ticks = F, title = expression(italic(A))))
}

```


```{r, fig.width = 5}
affinity_matrix_viz('Atlanta')
ggsave('figs/Atlanta_affinity.pdf')
```

```{r, fig.width = 5}
affinity_matrix_viz('Detroit')
ggsave('figs/Detroit_affinity.pdf')
```



```{r}

prominence_map <- function(tracts){
    tracts <- input$tracts

    demographics <- read_csv('data/demographics.csv') %>% 
        dplyr::mutate(tract = as.character(GEOID),
               tract = stringr::str_pad(tract, 12, side = 'left', pad = '0')) %>% 
        select(-GEOID) 
    
    data <- demographics %>% 
        filter(tract %in% tracts$GEOID)
    
    marginal <- data %>% 
        group_by(group) %>% 
        summarise(n = sum(n)) %>%
        mutate(n = n / sum(n))
    
    f <- function(df){
        df$group[which.max(df$n *  log(df$n / marginal$n))][1]
    }
    
    g <- function(df){
        max(df$n *  log(df$n / marginal$n), na.rm = T)
    }
    
    prominence_df <- data %>% 
        group_by(tract) %>% 
        mutate(n = n / sum(n)) %>% 
        nest(-tract, .key = df) %>% 
        mutate(prominent_group = map_chr(df, f),
               prominence = map_dbl(df, g)) 
        
    g <- tracts %>% fortify(region = 'GEOID') %>% 
          tbl_df() %>% 
          left_join(prominence_df, by = c('id' = 'tract')) %>% 
          ggplot() + 
          geom_polygon(aes(x = long, 
                           y = lat, 
                           fill = prominent_group, 
                           group = group, 
                           alpha = prominence))  +
          ggthemes::theme_map() + 
          scale_alpha_continuous(guide = 'none', limits = c(0,1)) +
          theme(plot.title = element_text(size=20, vjust = -5),
                legend.title = element_blank(),
                legend.position = c(.7, .1))
      g
}
```

Generate Detroit, with legend

```{r}
city  <- 'Detroit'
input <- readRDS(paste0('throughput/metric/', city, '.RDS'))

prominence_map(input$tracts) + 
    scale_fill_brewer(palette = 'Set1') 

ggsave('figs/detroit_prominence.pdf')
```

Generate Atlanta, no legend
```{r}
city  <- 'Atlanta'
input <- readRDS(paste0('throughput/metric/', city, '.RDS'))

prominence_map(input$tracts) + 
    scale_fill_brewer(palette = 'Set1') + 
    guides(fill = FALSE)

ggsave('figs/atlanta_prominence.pdf')
```

```{r}
city  <- 'Newark'
input <- readRDS(paste0('throughput/metric/', city, '.RDS'))

prominence_map(input$tracts) + 
    scale_fill_brewer(palette = 'Set1') + 
    guides(fill = FALSE)

ggsave('figs/newark_prominence.pdf')

```

# Session Info
```{r}
sessionInfo()
```

